State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-23 prism-backend/research/soa_review/ac.tex
Added review of HS21.

@@

@@

\begin{enumerate}
\item[\cite{cl01}:] Extensions provided to the main functionality are:
  \begin{itemize}
  \item PKI-based and all-or-nothing non-transferability: Both options
    involve sharing a verifiable encryption of the user secrets. In the
    case of PKI-based non-transferability, the CA receives a verifiable
    encryption, using as key the user's master secret, of some valuable
    piece of information belonging to the user (e.g., the user's secret
    key associated to his public key with that CA). In the all-or-nothing
    case, the user shares with each organization (with which it has a
    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
    with his master secret. In both cases, if the user shares his master
    secret with someone else, then he automatically gives access to
    other relevant pieces of information (as the verifiable encryptions are
    made public by the corresponding entity).    
  \item One-show credentials: The validating tags over pseudonyms are extended
    to include an extra value in their commitment. Then, users have to reveal
    that value (or, rather, a value deterministically derived from that) in the
    zero-knowledge proofs they create at show time. Since the value is always
    the same, verifiers can check whether they have seen it before, or not.
  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
    referring to an identity of the user in an external CA) is possible by
    extending the pseudonyms of the user, and the credential showing protocols,
    with values that allow subsequent decryption by a trusted party of their
    pseudonym or external identity, given a transcript of the credential
    showing.    
  \item Attributes: The paper also succinctly describes how multiple attributes
    per credential could be included. This would be done by dividing the inverval
    within the exponent used to compute the pseudonym in sub-intervals, and then
    proving that the exponent lies within a sub-interval.
  \end{itemize}
\item[\cite{cmz14}:] The paper mentions ``Credential translation'', which
  basically means being able to prove that two attributes in different
  credentials are actually the same. This is not formalized or detailed,
  though.
\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
\item[\cite{dmm+18}:] The scheme supports delegated verification. Basically,
  to implement delegated verification, the delegatee receives an encryption of
  the policy it has to verify, plus a signature of the encryption. If the
  signature is valid, it re-randomizes the ciphertext for the policy, and
  sends it to the user, who follows the same protocol as in the normal case.
  The paper also mentions how to add more functionality, like delegation of
  credentials and revocation, but they are not modelled. Also interestingly,
  they claim somewhat informally (in Section 2.3) that no scheme satisfying
  anonymity in the presence of an untrustworthy issuer can support delegation
  of verification with policy hiding.
\item[\cite{sms+19}:] It is essentially the same as previous works, although it
  supports threshold issuance. Interestingly, \cite{sms+19} does not make use
  of pseudonyms. I.e., credentials are just signed (blocks of) attributes. This
  probably lets them achieve better efficiency. \doubt{This makes the scheme
    to be practically like a group signature scheme (without revocation...)}
\end{enumerate}

@@

PS: Tokenization.
U-Prove.
Idemix.
Signal's AC \needcite

>>>>

\item[\cite{hs21}:] This work merges AC approaches based on SPS-EQ and aggregate
  signatures, and also introduces the separation between a trusted but restricted
  device, and a less trusted but powerful device typical in DAA systems. The
  former is referred to as \emph{core}, and the latter as \emph{helper}, hence
  the Core-Helper AC (CHAC) acronym. In addition to the previous basic building
  blocks, the system uses a Signature with Flexible Public Keys (SFPK) scheme.
  Roughly, these are signature schemes where the public keys can be randomized,
  but in a manner that no adversary can decide whether two public keys are
  related or not (i.e., if one is a randomization of the other). Users identities
  are SFPK keypairs, where the public part gets signed by the issuer, using an
  AAEQ scheme (Aggregatable Attribute-based Signature Scheme on Equivalence Classes).
  Roughly, an AAEQ scheme is a combination of attribute-based signatures on
  equivalence classes (which the authors combine with Tag-based Signatures on
  Equivalence Classes), and aggregate signatures. In the proposed AAEQ scheme,
  a tag is derived from an attribute an a nonce, which is then ``signed'' (note:
  this tag resembles much the concept of nyms based on scopes). Since signatures
  (and tags) are group elements sharing the same discrete log (the signer's key),
  they can be aggregated easily via multiplication. Hence, for each attribute that
  the issuer wants to grant to the user, it creates an independent signature where
  the tag depends on the attribute to grant. Then, the user can just aggregate
  all of them into one credential. In addition to this, the authors split the
  operations (which are in the bilinear setting), in a way that requires the
  core to perform only a few operations in $G_1$. The result seems to be quite
  efficient. However, it only supports selective disclosure (no advanced
  privacy-preserving policies), and even revocation is not considered from scratch,
  although the authors sketch an approach to integrate it -- which probably
  would require a more formal analysis and would incur in (possibly bad?)
  added costs.

@@

\item[\cite{hs21}:] Security is given through game-based definitions of
  unforgeability, anonymity, and dependability. The first two are the usual ones,
  while the latter roughly requires that an adversarial helper cannot produce
  successful showings without cooperation from the core. It would be interesting
  to make a detailed comparison with security models of DAA (usually in the UC
  framework, although some game-based (seemingly flawed) definitions exist).
  The main argument that the authors give when comparing to DAA, is that the
  latter does not support attributes, and it is essentially a group signature
  scheme without revocation and optional linkability (this frontier is also
  blurry, see \cite{dl21}).

@@

\begin{enumerate}
\item[\cite{cl01}:] Extensions provided to the main functionality are:
  \begin{itemize}
  \item PKI-based and all-or-nothing non-transferability: Both options
    involve sharing a verifiable encryption of the user secrets. In the
    case of PKI-based non-transferability, the CA receives a verifiable
    encryption, using as key the user's master secret, of some valuable
    piece of information belonging to the user (e.g., the user's secret
    key associated to his public key with that CA). In the all-or-nothing
    case, the user shares with each organization (with which it has a
    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
    with his master secret. In both cases, if the user shares his master
    secret with someone else, then he automatically gives access to
    other relevant pieces of information (as the verifiable encryptions are
    made public by the corresponding entity).    
  \item One-show credentials: The validating tags over pseudonyms are extended
    to include an extra value in their commitment. Then, users have to reveal
    that value (or, rather, a value deterministically derived from that) in the
    zero-knowledge proofs they create at show time. Since the value is always
    the same, verifiers can check whether they have seen it before, or not.
  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
    referring to an identity of the user in an external CA) is possible by
    extending the pseudonyms of the user, and the credential showing protocols,
    with values that allow subsequent decryption by a trusted party of their
    pseudonym or external identity, given a transcript of the credential
    showing.    
  \item Attributes: The paper also succinctly describes how multiple attributes
    per credential could be included. This would be done by dividing the inverval
    within the exponent used to compute the pseudonym in sub-intervals, and then
    proving that the exponent lies within a sub-interval.
  \end{itemize}
\item[\cite{cmz14}:] The paper mentions ``Credential translation'', which
  basically means being able to prove that two attributes in different
  credentials are actually the same. This is not formalized or detailed,
  though.
\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
\item[\cite{dmm+18}:] The scheme supports delegated verification. Basically,
  to implement delegated verification, the delegatee receives an encryption of
  the policy it has to verify, plus a signature of the encryption. If the
  signature is valid, it re-randomizes the ciphertext for the policy, and
  sends it to the user, who follows the same protocol as in the normal case.
  The paper also mentions how to add more functionality, like delegation of
  credentials and revocation, but they are not modelled. Also interestingly,
  they claim somewhat informally (in Section 2.3) that no scheme satisfying
  anonymity in the presence of an untrustworthy issuer can support delegation
  of verification with policy hiding.
\item[\cite{sms+19}:] It is essentially the same as previous works, although it
  supports threshold issuance. Interestingly, \cite{sms+19} does not make use
  of pseudonyms. I.e., credentials are just signed (blocks of) attributes. This
  probably lets them achieve better efficiency. \doubt{This makes the scheme
    to be practically like a group signature scheme (without revocation...)}
\item[\cite{hs21}:] The main variation here is the application of the core-helper
  division (typical of DAA) to the AC domain.
\end{enumerate}

@@

PS: Tokenization.
Signal's AC \cite{cpz20}.

\begin{itemize}
\item U-Prove (see ref. 65 in \cite{hs21}):  This is largely based on Brands
  thesis. There was a deployment by Microsoft, mostly concurrent to Idemix.
  They are one-show credentials, but seemingly there is recent real-world
  deployments based on them (references in p.1 of \cite{hs21}):

  \begin{itemize}
  \item Privacy-Pass by Cloudflare.
  \item Trust Tokens API by Google.
  \item PrivateStats proposal by Facebook.
  \end{itemize}

\item Idemix \cite{ch02}: This is largely based on CL signatures. It has been
  deployed (or is being deployed) in Hyperledger Fabric, and I think there is
  some of it in Indy too.
\end{itemize}

\cite{hs21} contains also many references to ``practical'' applications of
ACs. However, these are mostly references to papers in cryptographic venues,
so I suspect that they are more academic than real-world systems.
